The Linguistic Landscape of Stream-of-Consciousness Literature

### 2024-04-03 paper/paper.qmd
update paper

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-count
#| layout-ncol: 2
#| fig-cap: "Comparative Analysis of Top 20 Word Frequencies by Stream of Consciousness Authors' Novels"
#| fig-subcap: ["James Joyce", "Virginia Woolf", "Marcel Proust", "T.S. Eliot", "Katherine Mansfield"]

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-sentiment
#| fig-cap: "Sentiment Analysis of All Stream of Consciousness Books"

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-sentiment-number
#| fig-cap: "Sentiment Analysis of All Stream of Consciousness Books by Value"

@@

ggplot(frequency_female, aes(x = proportion, y = `Katherine Mansfield`, color = abs(`Katherine Mansfield` - proportion))) +
  geom_abline(color = "gray50", lty = 2) +
  geom_jitter(alpha = 0.1, size = 1, width = 0.5, height = 0.5) +  
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = scales::percent_format()) +
  scale_y_log10(labels = scales::percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslateblue", high = "gray50") +
  facet_wrap(~author, ncol = 1) +
  theme(legend.position="none") +
  labs(y = "Katherine Mansfield", x = NULL)

@@

ggplot(frequency_male, aes(x = proportion, y = `T.S. Eliot`, color = abs(`T.S. Eliot` - proportion))) +
  geom_abline(color = "gray50", lty = 2) +
  geom_jitter(alpha = 0.1, size = 1.5, width = 0.8, height = 0.8) +  
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslateblue", high = "gray100") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "T.S. Eliot", x = NULL)

@@

ggplot(frequency_international, aes(x = proportion, y = `Marcel Proust`, color = abs(`Marcel Proust` - proportion))) +
  geom_abline(color = "gray50", lty = 2) +
  geom_jitter(alpha = 0.05, size = 1, width = 0.8, height = 0.8) +  
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslateblue", high = "gray100") +
  facet_wrap(~author, ncol = 1) +
  theme(legend.position="none") +
  labs(y = "Marcel Proust", x = NULL)

>>>>

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-count
#| layout-ncol: 2
#| fig-cap: "Comparative Analysis of Top 20 Word Frequencies from Famous SOC Authors"
#| fig-subcap: ["James Joyce", "Virginia Woolf", "Marcel Proust", "T.S. Eliot", "Katherine Mansfield"]

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-sentiment
#| fig-cap: "Sentiment Analysis of All SOC Novels"

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-sentiment-number
#| fig-cap: "Sentiment Analysis of All SOC Novels by Sentiment Value"

@@

ggplot(frequency_female, aes(x = proportion, y = `Katherine Mansfield`, color = abs(`Katherine Mansfield` - proportion))) +
  geom_abline(color = "gray50", lty = 2) +
  geom_jitter(alpha = 0.1, size = 1, width = 0.5, height = 0.5) +  
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = scales::percent_format()) +
  scale_y_log10(labels = scales::percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "blue2", high = "gray50") +
  facet_wrap(~author, ncol = 1) +
  theme(legend.position="none") +
  labs(y = "Katherine Mansfield", x = NULL)

@@

ggplot(frequency_male, aes(x = proportion, y = `T.S. Eliot`, color = abs(`T.S. Eliot` - proportion))) +
  geom_abline(color = "gray50", lty = 2) +
  geom_jitter(alpha = 0.1, size = 1.5, width = 0.8, height = 0.8) +  
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "blue2", high = "gray100") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "T.S. Eliot", x = NULL)

@@

ggplot(frequency_international, aes(x = proportion, y = `Marcel Proust`, color = abs(`Marcel Proust` - proportion))) +
  geom_abline(color = "gray50", lty = 2) +
  geom_jitter(alpha = 0.05, size = 1, width = 0.8, height = 0.8) +  
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "blue2", high = "gray100") +
  facet_wrap(~author, ncol = 1) +
  theme(legend.position="none") +
  labs(y = "Marcel Proust", x = NULL)
